---
title: "session_6_demo"
author: "PeterPaziczki"
date: '2017 oktÄ‚Ĺ‚ber 29 '
output:
  html_document: default
---

```{r init, echo=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, error = TRUE)
```

Markdown is a **simple** *markup* language. Highlighting can be ***combined*** or ~~none~~.

Markdown is a **simple** *markup* language.
Highlighting
can
be ***combined*** or ~~none~~.

New paragraph.


```{r random-numbers}
n <- 1000
x <- rnorm(n, 10, 1)
```
We have just generated `r n` numbers:

```{r analysis}
summary(x)
hist(x)
```

```{r tables}
table(iris$Species)
library(knitr)
kable(head(iris))
kable(table(iris$Species)) # this won't run, because kable cannot handle tables

library(pander)
pander(table(iris$Species))

fit <- lm(Sepal.Width ~ Sepal.Length + Species, iris)
pander(fit)

```

TODO:
  
  - create a new R chunk: example
  - load the ggplot2 package (that includes the diamonds dataset)
  - render a table with average price of diamonds
  - render a boxplot on the prices of diamonds per cut quality


```{r example}
## we could write fig.width=7 or fig.heights=3, etc
## https://yihui.name/knitr/options/ is a great page where I can read about the option, Yihui is the author of knitr
library(ggplot2)
library(data.table)
dt <- data.table(diamonds)
pander(dt[,list(average_price = mean(price)), by = cut])
pander(dt[,list(average_price = mean(price)), by = cut], style = 'simple')
pander(dt[,list(average_price = mean(price)), by = cut], style = 'grid')
ggplot(dt, aes(cut, price)) + geom_boxplot()
```

```{r dynamic-chunk-example}
library(shiny)
inputPanel(
  sliderInput('n', label = 'N', min = 1, max = 1000, value = 100, step = 10)

)

renderPlot({
  hist(runif(as.numeric(input$n)))
})
```

```{r dynamic-chunk-example-2}
library(shiny)
inputPanel(
    sliderInput('n', label = 'N', min = 1, max = 1000, value = 100, step = 10),
    sliderInput('seed', label = 'Seed', min = 1, max = 42, value = 42, step = 1)) ## LATER

renderPlot({
  set.seed(as.numeric(input$seed)) ## LATER
  hist(runif(as.numeric(input$n)))
})
```
